---
title: "slide1"
author: "Andreia Vieira"
date: "05/07/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r , echo = TRUE}

library(leaflet)
library(dplyr)
quakes <- quakes %>%
  dplyr::mutate(mag.level = cut(mag,c(3,4,5,6),
                                labels = c('>3 & <=4', '>4 & <=5', '>5 & <=6')))

l <- leaflet() %>% addTiles()

quakes.df <- split(quakes, quakes$mag.level)
quakes.df

l2 <- l
names(quakes.df) %>%
  purrr::walk( function(df) {
    l2 <<- l2 %>%
      addMarkers(data=quakes.df[[df]],
                          lng=~long, lat=~lat,
                          label=~as.character(mag),
                          popup=~as.character(mag),
                          group = df,
                          clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                          labelOptions = labelOptions(noHide = T,
                                                       direction = 'auto'))
  })

l2 %>%
  addLayersControl(
    overlayGroups = names(quakes.df),
    options = layersControlOptions(collapsed = FALSE)
  )








```

## Slide with Plot

```{r pressure}
plot(pressure)
```

